Staged Abstract Interpreter

### 2018-01-05 paper.tex
outline

\textbf{Contribution(Proposed)}.

@@

We implement staged abstract interpreter in a big-step semantics (abstract definitional interpreter) 
using Scala with LMS framework. Show it generates sound and high-performance analysis code with 
various precisions and sensitivities, for examples, k-CFA, pushdown or m-CFA. 
Generate efficient store implementation.

Show the evaluation result on benchmark programs.

Can we do it with small-step semantics? or staging a transition system?

Modular analysis? For example, k-CFA (k > 0) is a naturally global program analysis, because 
it need the last k calling contexts. But can we analyze programs (libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

@@

\textbf{Abstract Compilation}. The idea in this paper was closely inspired by 
abstract compilation \cite{Boucher:1996:ACN:647473.727587}.
\citeauthor{Boucher:1996:ACN:647473.727587} presented abstract compilation
techniques as an efficient implementation of the monovariant flow analysis 
\textit{0}-CFA for programs in continuation-passing style. The key idea is to 
reduce the interpretation overhead on traversing the syntax tree by partial evaluation.
Specifically, they proposed two kinds of abstract compilers to achieve this. 
The first one is to generate specialized analysis as a textual program, then 
can be loaded and executed by \texttt{eval} or similar mechanisms. The second 
one is using closure as a representation of specialized analysis. 
A closure is a function that remembers the environment where it defined. So the 
abstract compiler generates higer-order functions on-the-fly rather than textual 
program, then the functions can be executed immediately in a higher-order language.

>>>>

\textbf{Outline(Proposed)}.

1. Revisit abstract compilation (generates textual program and closures)

@@

2. But closure is still not an efficient enough representation.

We implement staged abstract interpreter in a big-step semantics (abstract definitional interpreter) 
using Scala with LMS framework.  
Show it generates sound and high-performance low-level analysis code with 
various precisions and sensitivities, for instances, k-CFA, pushdown or m-CFA.

Store/set operations (join, update) is expensive. Generate efficient store implementation\cite{liang2014fast}.

Extension: can we do it with small-step semantics? or staging a transition system?

3. Modular analysis for free?

For example, k-CFA (k > 0) is a naturally global program analysis, because 
it need the last k calling contexts. But can we analyze programs (or libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

For another example, programs are data for an abstract interpreter, if we have $n$ programs, then there 
are $n$ stages. Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.

Not sure how much improvement of performance.

4. Show the evaluation result on benchmark programs.

@@

\textbf{Abstract Compilation}. The idea in this paper was closely inspired by 
abstract compilation \cite{Boucher:1996:ACN:647473.727587}.
\citeauthor{Boucher:1996:ACN:647473.727587} presented abstract compilation
techniques as an efficient implementation of the monovariant flow analysis 
\textit{0}-CFA for programs in continuation-passing style. The key idea is to 
reduce the interpretation overhead on traversing the syntax tree by partial evaluation.
Specifically, they proposed two kinds of abstract compilers to achieve this. 
The first one is to generate specialized analysis as a textual program, then 
can be loaded and executed by \texttt{eval} or similar mechanisms. The second 
one is using closure as a representation of specialized analysis. 
A closure is a function that remembers the environment where it defined. So the 
abstract compiler generates higer-order functions on-the-fly rather than textual 
program, then the functions can be applied immediately in a higher-order host language.
